Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-08-05 Report/kkt_mse_approach.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
&\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}. The equality of \eqref{kkt-mse-1.2} is due to the equivalence of the \ac{MSE} expression with the transmit and the receive precoders.

By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \Big ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \Big ). \IEEEyessubnumber \label{kkt-mse-4.1}
\end{IEEEeqnarray}
The dual variable \me{\alpha^{(i)}} is updated with memory as in \eqref{kkt-mse-4.1} to avoid abrupt oscillations due to \me{\sigma < 0} from \eqref{kkt-mse-4.2} when \me{Q_k < \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}. The parameter \me{\rho \in [0,1]} provides a linear combination of the previous to the current value of the dual variable, dictating system reaction for the excess allocation.

@@

The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{W}{k,n}} evaluated at the receivers. Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{W}{k,n}^{\herm \, (i-1)} \mvec{H}{b,k,n}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}. The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
 set the maximum iteration counter \me{I_{\max}} to a valid number \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
	evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} by \eqref{kkt-mse-4.6} \;
	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
	$i = i + 1$ \;
  }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
  \label{algo-4}
\end{algorithm}

>>>>

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \\ \nonumber
&\hspace{0.5cm}& \qquad {} \qquad {} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}. The equality of \eqref{kkt-mse-1.2} is due to the equivalence of the \ac{MSE} expression with the transmit and the receive precoders.

By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \frac{\left [ \sigma_{l,k,n}^{(i)} \right ]^+}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}
The dual variable \me{\alpha^{(i)}} is updated with memory as in \eqref{kkt-mse-4.1} to avoid abrupt oscillations due to \me{\sigma < 0} from \eqref{kkt-mse-4.2} when \me{Q_k < \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}. The parameter \me{\rho \in [0,1]} provides a linear combination of the previous to the current value of the dual variable, dictating system reaction for the excess allocation.

@@

The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}} evaluated at the receivers. Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\sqrt{\alpha_{l,k,n}^{(i-1)}} \mvec{w}{l,k,n}^{\ast \, (i-1)} \mvec{H}{b,k,n}^{\mathrm{T}}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}, \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}. The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
 set the maximum iteration counter \me{I_{\max}} to a valid number. \;
 \Repeat{until convergence or \me{j \geq J_{\max}}}{
 \lForEach{\ac{BS} \me{b \in \mc{B}}}
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
	update the \ac{MSE} \me{\epsilon_{l,k,n}^{(i)}} and the throughput \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}. \;
	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2}. \;
	$i = i + 1.$ \;
  }
  \me{j = j + 1}. \;
  evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6}. \;
  exchange the receive precoders \me{\mvec{W}{k,n}^{(i)}} and the dual variables \me{\alpha_{l,k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} using the uplink precoded pilots. \;
  }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
  \label{algo-4}
\end{algorithm}

\subsubsection*{Convergence}
The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge. The convergence of the dual variable is guaranteed, since the problem is convex once we fix the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}. Once the dual variables are converged or iterated to a certain accuracy, the receivers are updated using the \ac{MMSE} objective. In this algorithm, when \me{t_k > Q_k},

### 2014-08-05 Report/mse_formulation.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

In this section, we present an alternative approach for solving the \acl{QM} \ac{JSFRA} problem by using the \ac{MSE} equivalence with the the achievable capacity presented in \cite{viswanath1999optimal,mse_duality}. It is given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon(\gamma)} \right )}, where \me{\epsilon(\gamma) = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbol at the reciever employing the \ac{MMSE} equalizer and \me{C(\gamma)} is the achievable capacity for the \ac{SINR} of \me{\gamma}. Using this equivalence, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}. In this, we use the relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.

The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}. In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}. The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}.
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}

>>>>

In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}. The \ac{MSE} for the data symbol, represented as \me{\epsilon_{l,k,n}}, is given by
\begin{subeqnarray} \label{mse-error}
\epsilon_{l,k,n} &=& \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] \\
 &=&  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
\end{subeqnarray}
where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}. Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = \dfrac{1}{1 + \gamma_{l,k,n}}
\end{equation}
where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.

The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}. In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}. The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}
\end{IEEEeqnarray}
